Figures and Analysis for 2023 Manuscript

### 2023-10-24 data-raw/Manuscript2023_Workflow.Rmd
Markdown changes and calculating proportion of timepoints that are replicated vs non-replicated per data series.

>>>>

all_my_data %>%
  filter(Detect %in% TRUE,
         exclude %in% FALSE,
         Dose > 0) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route, 
           Media,
           Dose, Time) %>%
  count() %>%
  mutate(Replicated = ifelse(n > 1, TRUE, FALSE)) %>%
  distinct() %>% .$Replicated %>% table()
  ggplot(aes(fill = Replicated)) +
  geom_bar(position = "stack",
           color = "black")
  labs(x = "", y = "Timepoints") +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, NA)) +
  theme_void() +
  theme(legend.position = "bottom")
